\textsf{Are large language models superhuman chemists?}

### 2024-10-16 src/tex/appendix.tex
add radar plots back in

% \begin{figure}[htb]
%     \centering
%     \includegraphics{figures/overall_performance.pdf}
%     \caption{\textbf{Overall performance of the models on the \chembench corpus.} The bar plot shows the fraction of questions that were answered completely correctly by the models. Scores computed on the entire \chembench corpus.}
%     \label{fig:barplot_all_correct_all_questions}
%     \script{plot_overview_performance_plot.py}
% \end{figure}

@@

% \begin{figure}[htb]
%     \centering
%     \includegraphics{figures/all_questions_models_completely_correct_radar_overall.pdf}
%     \caption{\textbf{Performance of the models on the different topics of the \chembench corpus.} The radar plot shows the performance of the models on the different topics of the \chembench corpus. The performance is measured as the fraction of questions answered completely correctly by the models.
%     A score of 1 indicates that all questions were answered completely correctly, while a score of 0 indicates that none were answered completely correctly.
%     }
%     \label{fig:all_questions_models_completely_correct_radar_overall}
%     \script{analyze_model_reports.py}
% \end{figure}

\Cref{fig:parallel_coordinates_overall} shows this data as a parallel coordinates plot. 
This visualization highlights the critical observation that the ranking of the models highly depends on the questions they are evaluated on.
Only very broad benchmarks have the potential to provide a comprehensive view of a model's capabilities. However, even in those cases, the weighting of the different topics is crucial.
Hence, we believe that fine-grained analysis of model performance is vital for the development of future benchmarks.

% \begin{figure}[htb]
%     \centering
%     \includegraphics{figures/parallel_coordinates_overall.pdf}
%     \caption{\textbf{Performance of the models on the different topics of the \chembench corpus.} The parallel coordinates plot shows the performance of the models on the different topics of the \chembench corpus. The performance is measured as the fraction of questions answered completely correctly by the models. }
%     \label{fig:parallel_coordinates_overall}
%     \script{make_parallel_coordinates_plot.py}
% \end{figure}

% \begin{figure}[htb]
%     \centering
%     \includegraphics{figures/parallel_coordinates_tiny.pdf}
%     \caption{\textbf{Performance of the models on the different topics of the \enquote{tiny} subset.} The parallel coordinates plot shows the performance of the models on the different topics of the \enquote{tiny} subset. The performance is measured as the fraction of questions answered completely correctly by the models. }
%     \label{fig:parallel_coordinates_tiny}
%     \script{make_parallel_coordinates_plot.py}
% \end{figure}

@@

% \begin{figure}[htb]
%     \centering
%     \includegraphics{figures/performance_per_topic_tiny.pdf}
%     \caption{\textbf{Fraction of completely correctly answered questions per data source on the \enquote{tiny} subset.} The heatmap shows, in color, the fraction of questions answered completely correctly by different systems for some of our data sources. The performance is measured as the fraction of questions answered completely correctly by the models. A score of one (red) indicates that all questions were answered completely correctly, while a score of zero (blue) indicates that none were answered completely correctly.
%         We see that the performance of the models varies significantly between the different data sources. For instance, it is interesting to observe that questions sourced based on textbooks seem easier for the leading models than for humans. However, this performance does not correlate with performance on other sources, e.g., semi-programmatically created tasks such as questions about the number of signals in an \gls{nmr} spectrum.
%     }
%     \label{fig:performance_per_topic_tiny}
%     \script{analyze_performance_per_source.py}
% \end{figure}

One might wonder if questions that are more difficult to parse lead to worse performance of the models.
\Cref{fig:reading_ease_vs_model_performance} shows no clear correlation between the reading ease of the questions and the performance of the models.

\begin{figure}
    \centering
    \hspace*{-1cm}
    \includegraphics{figures/reading_ease_vs_model_performance.pdf}
    \caption{\textbf{Model performance as a function of reading ease.} The violin plots show the distribution of reading ease scores for questions answered completely correctly and those not. We do not observe a clear correlation between the reading ease of the questions and the performance of the models. }
    \script{reading_ease_vs_model_performance.py}
    \label{fig:reading_ease_vs_model_performance}
\end{figure}

@@

% \begin{figure}[htb]
%     \centering
%     \includegraphics{figures/human_score_distribution.pdf}
%     \script{plot_human_score_distribution.py}
%     \caption{\textbf{Distribution of human scores.} The histogram and kernel density estimates show the fraction of questions answered completely correctly.
%     Since the best possible score for each question is one and the worst possible score is zero, the values on this plot are between zero and one.}
%     \label{fig:human_score_distribution}
% \end{figure}

>>>>

\begin{figure}[htb]
    \centering
    \includegraphics{figures/overall_performance.pdf}
    \caption{\textbf{Overall performance of the models on the \chembench corpus.} The bar plot shows the fraction of questions that were answered completely correctly by the models. Scores computed on the entire \chembench corpus.}
    \label{fig:barplot_all_correct_all_questions}
    \script{plot_overview_performance_plot.py}
\end{figure}

@@

\begin{figure}[htb]
    \centering
    \includegraphics{figures/all_questions_models_completely_correct_radar_overall.pdf}
    \caption{\textbf{Performance of the models on the different topics of the \chembench corpus.} The radar plot shows the performance of the models on the different topics of the \chembench corpus. The performance is measured as the fraction of questions answered completely correctly by the models.
    A score of 1 indicates that all questions were answered completely correctly, while a score of 0 indicates that none were answered completely correctly.
    }
    \label{fig:all_questions_models_completely_correct_radar_overall}
    \script{analyze_model_reports.py}
\end{figure}

@@

\begin{figure}[htb]
    \centering
    \includegraphics{figures/performance_per_topic_tiny.pdf}
    \caption{\textbf{Fraction of completely correctly answered questions per data source on the \enquote{tiny} subset.} The heatmap shows, in color, the fraction of questions answered completely correctly by different systems for some of our data sources. The performance is measured as the fraction of questions answered completely correctly by the models. A score of one (red) indicates that all questions were answered completely correctly, while a score of zero (blue) indicates that none were answered completely correctly.
        We see that the performance of the models varies significantly between the different data sources. For instance, it is interesting to observe that questions sourced based on textbooks seem easier for the leading models than for humans. However, this performance does not correlate with performance on other sources, e.g., semi-programmatically created tasks such as questions about the number of signals in an \gls{nmr} spectrum.
    }
    \label{fig:performance_per_topic_tiny}
    \script{analyze_performance_per_source.py}
\end{figure}

@@

\begin{figure}[htb]
    \centering
    \includegraphics{figures/human_score_distribution.pdf}
    \script{plot_human_score_distribution.py}
    \caption{\textbf{Distribution of human scores.} The histogram and kernel density estimates show the fraction of questions answered completely correctly.
    Since the best possible score for each question is one and the worst possible score is zero, the values on this plot are between zero and one.}
    \label{fig:human_score_distribution}
\end{figure}
